Supplementary Materials

### 2020-05-26 analysis/analysis.Rmd
trying to fix subgroup comp functions

```{r subgroup_comparisons, cache=TRUE}
source("scripts/get_subgroup_comparisons.R")

subgroup_comp$eeg <- get_subgroup_comparisons(my_samples$eeg, 2*n_iter)
subgroup_comp$threshold <- get_subgroup_comparisons(my_samples$threshold, 2*n_iter)
subgroup_comp$occ_even <- get_subgroup_comparisons(my_samples$occ_even, 2*n_iter)
subgroup_comp$par_odd  <- get_subgroup_comparisons(my_samples$par_odd,  2*n_iter)
```

>>>>

```{r subgroup_comparisons}
source("scripts/get_subgroup_comparisons.R")

subgroup_comp$eeg <- get_subgroup_comparisons2(my_samples$eeg)
subgroup_comp$threshold <- get_subgroup_comparisons2(my_samples$threshold,)
subgroup_comp$occ_even <- get_subgroup_comparisons2(my_samples$occ_even)
subgroup_comp$par_odd  <- get_subgroup_comparisons2(my_samples$par_odd)
```
